A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-08 03_smoothing_tracks.Rmd
better aggregate track

```{r}
### plot figures
fig_agg_data <- 
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      geom_point(data = data_errors,
                 aes(x, y),
                 size = 0.2,
                 col = pal[3])+
            geom_path(data = data,
                aes(x, y),
                lwd = 0.3)+
      geom_path(aes(x,y), 
                col = pal[1],
                lwd = 0.2)+
      geom_point(aes(x,y, 
                     size = SD,
                     fill = speed,
                     group = interval),
                 shape = 16,
                 show.legend = F)+
      scale_fill_distiller(palette = "Purples", direction = 1,
                             values = c(-0.25, 1))+
        ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "grey99"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

# show boxplot of speed
fig_agg_speed <- ggplot(data_agg)+
  geom_jitter(aes(factor(interval), speed),
              col = "grey",
              shape = 4, alpha = 0.5)+
  geom_boxplot(aes(factor(interval), speed),
               fill = NA,
               show.legend = F, 
               width = 0.3, 
               outlier.size = 0.2)+
  geom_hline(yintercept =
               c(mean(data$speed, na.rm = T),
                 quantile(data$speed, na.rm = T,
                          probs = c(0.95))
               ),
             lty = c(1, 2))+
  scale_y_log10(label = scales::comma)+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r}
# make combined figure
fig_aggregate <- 
  wrap_plots(append(fig_agg_data[2:3], list(fig_agg_speed)),
           design = "AAABBBCC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

# save figure
ggsave(fig_aggregate,
       filename = "figures/fig_aggregate_errors.png",
       width = 170, height = 170 / 1.67, units = "mm")
```

>>>>

```{r}
### plot figures
fig_agg_data <- 
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      geom_point(data = data_errors,
                 aes(x, y),
                 size = 0.2,
                 col = pal[3])+
      geom_path(data = data,
                aes(x, y),
                lwd = 0.3)+
      geom_path(aes(x,y), 
                col = pal[1])+
      geom_point(aes(x,y, 
                     size = SD,
                     fill = SD,
                     group = interval),
                 shape = 21,
                 alpha = 0.8,
                 show.legend = F)+
      scale_fill_distiller(palette = "RdPu", direction = 1,
                           values = c(-0.25, 1))+
      scale_size(range = c(2, 4))+
      ggthemes::theme_few()+
      theme(axis.text = element_blank(),
            axis.title = element_blank(),
            panel.background = element_rect(fill = "grey99"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_jitter(aes(factor(interval), speed),
              col = pal[1],
              shape = 4, alpha = 0.5)+
  geom_boxplot(aes(factor(interval), speed),
               fill = NA,
               show.legend = F, 
               width = 0.3, 
               outlier.size = 0.2)+
  geom_hline(yintercept =
               c(mean(data$speed, na.rm = T),
                 quantile(data$speed, na.rm = T,
                          probs = c(0.95))
               ),
             lty = c(1, 2))+
  scale_y_log10(label = scales::comma)+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r}
# make combined figure
fig_aggregate <-
  wrap_plots(append(fig_agg_data[3:4], list(fig_agg_speed)),
           design = "AABBC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

# save figure
ggsave(fig_aggregate,
       filename = "figures/fig_aggregate_errors.png",
       width = 170, height = 85, units = "mm")
```
